Appendix

### 2025-10-28 manuscript_rmarkdown/manuscript_appendix.Rmd
Update manuscript_appendix.Rmd

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests for features from simulated clean data without outliers after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.}
\label{tab:clean-transformation-appendix-p-value-yj}
\small{
\begin{tabular}{p{3.5cm} | l r r r r r r r r r}

@@

none                                  & & 0.981 & 0.816 & 0.576 & $<0.001$ & 0.099 & 0.011 & $<0.001$ & 0.993 & $<0.001$ \\
conventional                          & & 0.979 & 0.614 & 0.617 &   0.722  & 0.221 & 0.782 &   0.946  & 0.997 &   0.637 \\
conventional (z-score norm.)          & & 0.970 & 0.594 & 0.645 &   0.251  & 0.224 & 0.895 &   0.529  & 0.998 &   0.828 \\
conventional (robust scaling)         & & 0.974 & 0.593 & 0.640 &   0.538  & 0.207 & 0.837 &   0.933  & 0.998 &   0.810 \\
Raymaekers-Rousseeuw                  & & 0.983 & 0.614 & 0.617 &   0.722  & 0.622 & 0.782 &   0.927  & 0.985 &   0.831 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.985 & 0.594 & 0.645 &   0.251  & 0.623 & 0.895 &   0.564  & 0.984 &   0.807 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.987 & 0.593 & 0.640 &   0.538  & 0.599 & 0.837 &   0.935  & 0.984 &   0.875 \\
invariant                             & & 0.987 & 0.487 & 0.573 &   0.778  & 0.241 & 0.683 &   0.963  & 0.997 &   0.865 \\
robust invariant                      & & 0.992 & 0.753 & 0.667 &   0.909  & 0.739 & 0.628 &   0.968  & 0.994 &   0.680 \\

@@

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests for features from simulated clean data without outliers after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.}
\label{tab:clean-transformation-appendix-p-value-bc}
\small{
\begin{tabular}{p{3.5cm} | l r r r r r r r r r}

@@

none                                  & & 0.940 & 0.816 & 0.498 & $<0.001$ & 0.098 & 0.714 & $<0.001$ & 0.993 & 0.928 \\
conventional                          & & 0.948 & 0.695 & 0.603 &   0.798  & 0.163 & 0.791 &   0.931  & 0.997 & 0.658 \\
conventional (z-score norm.)          & & 0.947 & 0.777 & 0.624 &   0.611  & 0.182 & 0.788 &   0.969  & 0.991 & 0.822 \\
conventional (robust scaling)         & & 0.947 & 0.777 & 0.624 &   0.611  & 0.182 & 0.788 &   0.969  & 0.991 & 0.822 \\
Raymaekers-Rousseeuw                  & & 0.948 & 0.695 & 0.603 &   0.798  & 0.768 & 0.806 &   0.816  & 0.962 & 0.782 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.947 & 0.777 & 0.753 &   0.913  & 0.255 & 0.784 &   0.775  & 0.866 & 0.921 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.947 & 0.777 & 0.753 &   0.913  & 0.255 & 0.784 &   0.807  & 0.866 & 0.921 \\
invariant                             & & 0.947 & 0.661 & 0.624 &   0.611  & 0.182 & 0.789 &   0.956  & 0.997 & 0.664 \\
robust invariant                      & & 0.969 & 0.824 & 0.750 &   0.972  & 0.779 & 0.775 &   0.956  & 0.934 & 0.840 \\

@@

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests for features from real-world datasets after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling. 
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value}
\begin{tabular}{l | r r r r r}

@@

none                                  & 0.694 & 0.832     & 0.727     & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.961 & 0.003     & $< 0.001$ & $< 0.001$ & 0.101 \\
conventional (z-score norm.)          & 0.919 & 0.021     & $< 0.001$ & $< 0.001$ & 0.099 \\
conventional (robust scaling)         & 0.933 & $< 0.001$ & $< 0.001$ & $< 0.001$ & 0.129 \\
Raymaekers-Rousseeuw                  & 0.961 & 0.881     & 0.373     & $< 0.001$ & 0.101 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.694 & 0.899     & 0.809     & $< 0.001$ & 0.099 \\
Raymaekers-Rousseeuw (robust scaling) & 0.900 & 0.880     & 0.811     & $< 0.001$ & 0.144 \\
invariant                             & 0.976 & 0.147     & $< 0.001$ & $< 0.001$ & 0.276 \\
robust invariant                      & 0.933 & 0.178     & 0.759     & $< 0.001$ & 0.688 \\

@@

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling. 
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value-bc}
\begin{tabular}{l | r r r r r}

@@

none                                  & 0.694 & 0.832 & 0.727     & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.961 & 0.002 & $< 0.001$ & $< 0.001$ & 0.101 \\
conventional (z-score norm.)          & 0.901 & 0.005 & $< 0.001$ & $< 0.001$ & 0.154 \\
conventional (robust scaling)         & 0.901 & 0.005 & $< 0.001$ & $< 0.001$ & 0.154 \\
Raymaekers-Rousseeuw                  & 0.961 & 0.871 & 0.365     & $< 0.001$ & 0.101 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.891 & 0.268 & $< 0.001$ & $< 0.001$ &	0.495 \\
Raymaekers-Rousseeuw (robust scaling) & 0.562 & 0.789 & $< 0.001$ & $< 0.001$ &	0.492 \\
invariant                             & 0.962 & 0.004 & $< 0.001$ & $< 0.001$ &	0.154 \\
robust invariant                      & 0.899 & 0.890 & 0.866     & $< 0.001$ & 0.622 \\

>>>>

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests ($\kappa = 0.80$) for features from simulated clean data without outliers after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.}
\label{tab:clean-transformation-appendix-p-value-yj}
\small{
\begin{tabular}{p{3.5cm} | l r r r r r r r r r}

@@

none                                  & & 0.968 & 0.742 & 0.450 & $<0.001$ & 0.058 & 0.004 & $<0.001$ & 0.963 & $<0.001$ \\
conventional                          & & 0.966 & 0.494 & 0.498 &   0.632  & 0.145 & 0.707 &   0.828  & 0.986 &   0.358 \\
conventional (z-score norm.)          & & 0.955 & 0.471 & 0.529 &   0.169  & 0.147 & 0.853 &   0.260  & 0.986 &   0.603 \\
conventional (robust scaling)         & & 0.957 & 0.470 & 0.523 &   0.674  & 0.146 & 0.775 &   0.828  & 0.986 &   0.347 \\
Raymaekers-Rousseeuw                  & & 0.972 & 0.494 & 0.498 &   0.632  & 0.518 & 0.707 &   0.785  & 0.939 &   0.609 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.974 & 0.471 & 0.529 &   0.169  & 0.519 & 0.853 &   0.289  & 0.935 &   0.568 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.968 & 0.470 & 0.523 &   0.674  & 0.536 & 0.775 &   0.762  & 0.935 &   0.609 \\
invariant                             & & 0.978 & 0.353 & 0.448 &   0.701  & 0.161 & 0.588 &   0.872  & 0.984 &   0.667 \\
robust invariant                      & & 0.985 & 0.660 & 0.556 &   0.871  & 0.652 & 0.525 &   0.888  & 0.968 &   0.411 \\

@@

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests ($\kappa = 0.80$) for features from simulated clean data without outliers after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.}
\label{tab:clean-transformation-appendix-p-value-bc}
\small{
\begin{tabular}{p{3.5cm} | l r r r r r r r r r}

@@

\midrule
none                                  & & 0.911 & 0.742 & 0.365 & $<0.001$ & 0.057 & 0.623 & $<0.001$ & 0.962 & 0.789 \\
conventional                          & & 0.922 & 0.590 & 0.482 &   0.726  & 0.100 & 0.718 &   0.794  & 0.984 & 0.380 \\
conventional (z-score norm.)          & & 0.920 & 0.690 & 0.506 &   0.505  & 0.114 & 0.714 &   0.888  & 0.957 & 0.594 \\
conventional (robust scaling)         & & 0.920 & 0.690 & 0.506 &   0.504  & 0.114 & 0.714 &   0.887  & 0.957 & 0.594 \\
Raymaekers-Rousseeuw                  & & 0.922 & 0.590 & 0.482 &   0.726  & 0.689 & 0.736 &   0.582  & 0.869 & 0.531 \\
Raymaekers-Rousseeuw (z-score norm.)  & & 0.920 & 0.690 & 0.660 &   0.876  & 0.172 & 0.710 &   0.521  & 0.670 & 0.774 \\
Raymaekers-Rousseeuw (robust scaling) & & 0.920 & 0.690 & 0.660 &   0.876  & 0.172 & 0.710 &   0.568  & 0.670 & 0.774 \\
invariant                             & & 0.921 & 0.549 & 0.506 &   0.505  & 0.114 & 0.715 &   0.853  & 0.986 & 0.387 \\
robust invariant                      & & 0.954 & 0.752 & 0.656 &   0.956  & 0.699 & 0.698 &   0.852  & 0.801 & 0.623 \\

@@

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests ($\kappa = 0.80$) for features from real-world datasets after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling. 
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value}
\begin{tabular}{l | r r r r r}

@@

none                                  & 0.541 &    0.731  &    0.546  & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.919 & $< 0.001$ & $< 0.001$ & $< 0.001$ &    0.032 \\
conventional (z-score norm.)          & 0.845 &    0.007  & $< 0.001$ & $< 0.001$ &    0.031 \\
conventional (robust scaling)         & 0.847 & $< 0.001$ & $< 0.001$ & $< 0.001$ &    0.063 \\
Raymaekers-Rousseeuw                  & 0.919 &    0.802  &    0.205  & $< 0.001$ &    0.032 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.540 &    0.830  &    0.655  & $< 0.001$ &    0.031 \\
Raymaekers-Rousseeuw (robust scaling) & 0.438 &    0.878  &    0.669  & $< 0.001$ &    0.064 \\
invariant                             & 0.947 &    0.071  & $< 0.001$ & $< 0.001$ &    0.123 \\
robust invariant                      & 0.867 &    0.091  &    0.587  & $< 0.001$ &    0.477 \\

@@

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests ($\kappa = 0.80$) for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling. 
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value-bc}
\begin{tabular}{l | r r r r r}

@@

none                                  & 0.541 &    0.731  &    0.546  & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.919 & $< 0.001$ & $< 0.001$ & $< 0.001$ &    0.032 \\
conventional (z-score norm.)          & 0.815 &    0.001  & $< 0.001$ & $< 0.001$ &    0.057 \\
conventional (robust scaling)         & 0.815 &    0.001  & $< 0.001$ & $< 0.001$ &    0.057 \\
Raymaekers-Rousseeuw                  & 0.919 &    0.787  &    0.200  & $< 0.001$ &    0.032 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.799 &    0.152  & $< 0.001$ & $< 0.001$ &    0.285 \\
Raymaekers-Rousseeuw (robust scaling) & 0.799 &    0.674  &    0.060  & $< 0.001$ &    0.285 \\
invariant                             & 0.919 &    0.001  & $< 0.001$ & $< 0.001$ &    0.057 \\
robust invariant                      & 0.813 &    0.817  &    0.736  & $< 0.001$ &    0.403 \\
